One page description

### 2016-12-07 publications/Journal/4-performance.tex

\begin{figure}
    \center
	\includegraphics[width=\modelfraction\columnwidth]{fig/phold_model.pdf}
	\caption{PHOLD model for three models.}
	\label{fig:PHOLD_model}
\end{figure}

\subsection{Signle Core Simulation}
We start by evaluating single core simulation performance, in order to obtain a baseline for our comparison of multi core simulation performance.

>>>>

\begin{figure}
    \center
	\includegraphics[width=\modelfraction\columnwidth]{fig/phold_model.pdf}
	\caption{PHOLD model for four models. Color denotes the two nodes.}
	\label{fig:PHOLD_model}
\end{figure}

\subsection{Single Core Simulation}
We start by evaluating single core simulation performance, in order to obtain a baseline for our comparison of multi core simulation performance.
